Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/motivation.tex
motivation nits

Similarly, the infamous Android master key bug~\cite{saurik-masterkey} completely bypassed Android
security exploited parser inconsistencies
between the ZIP handler that checks signatures for privileged applications and the ZIP
implementation that ultimately extract those files. Thus, privileged application bundles could be
modified to include malicious code without breaking their signatures. Google quickly fixed this
particular parser inconsistency, but another vulnerability, based on a different inconsistency
between the parsers, was quickly disclosed~\cite{saurik-masterkey2}.

@@

Android application bundles are based on ZIP files, so we decided to conduct a systematic studies of
vulnerabilities related to ZIP parsing.  
The ZIP format has been associated with many vulnerabilities, and the
PROTOS Genome project~\cite{protos-c10-archive} found numerous security vulnerabilities in most
implementations of ZIP and other archive formats that are directly
related to input handling. We extend this study by looking at the CVE database.

\input{fig-motivation}
Figure~\ref{fig:motivation} shows  the 83 vulnerabilities the CVE database~\cite{cve-database} lists
 for the search string ``ZIP''. 16 of these vulnerabilities are related to processing .ZIP archives
 themselves; the rest are either totally unrelated to .ZIP archives or involve applications insecurely using
 the contents of untrusted ZIP files.

These input processing vulnerabilities fall into two broad classes.  The first
class, which occurred 11 times, is memory safety bugs, such as buffer overflows, which allow an
adversary to corrupt the application's memory using specially crafted
inputs.  These mistakes arise in lower-level languages that do not
provide memory safety guarantees such as C, and can be partially
mitigated by a wide range of techniques, for example static analysis,
dynamic instrumentation, and address space layout randomization, that
make it more difficult for an adversary to exploit these bugs.
Nail helps developers of lower-level languages avoid these bugs
in the first place.

The second class, which occurred four times in our study is logic errors, where application code
misinterprets input data. Safe languages and exploit mitigation technologies do not help against
such vulnerabilities. This can lead to serious security consequences when two systems disagree on
the meaning of a network packet or a signed message, as shown by the vulnerabilities we described
before. CVE-2013-0211 shows that logic errors can be the underlying cause of memory corruption, when
one part of a parser interprets a size field as a signed integer and another interprets it as an
unsigned integer. CVE-2013-7338 is a logic error that allows an attacker to craft ZIP files that are
incorrectly extracted or result in application hangs with applications using a Python ZIP library,
because this library does not check that two fields that contain the size of a file contain the same value.

>>>>

Similarly, the infamous Android master key bug~\cite{saurik-masterkey} completely bypassed Android
security by exploiting parser inconsistencies
between the ZIP handler that checks signatures for privileged applications and the ZIP
implementation that ultimately extracts those files. Thus, privileged application bundles could be
modified to include malicious code without breaking their signatures. Google quickly fixed this
particular parser inconsistency, but another vulnerability, based on a different inconsistency
between the parsers, was quickly disclosed~\cite{saurik-masterkey2}.

@@

To understand the impact of parsing mistakes in real-world software,
we conducted a systematic study of
vulnerabilities related to ZIP file parsing.  
The ZIP format has been associated with many vulnerabilities, and the
PROTOS Genome project~\cite{protos-c10-archive} found numerous security vulnerabilities in most
implementations of ZIP and other archive formats that are directly
related to input handling. We extend this study by looking at the CVE database.

\input{fig-motivation}

We found 83 vulnerabilities in the CVE database~\cite{cve-database} that
that mention the search string ``ZIP.''  Just 16 of these vulnerabilities
were related to processing ZIP archives; the rest were unrelated to ZIP
archives or involved applications insecurely using the contents of untrusted
ZIP files.  Figure~\ref{fig:motivation} summarizes the 16 ZIP-related
vulnerabilities.

These input processing vulnerabilities fall into two broad classes.  The first
class, which occurred 11 times, is memory safety bugs, such as buffer overflows, which allow an
adversary to corrupt the application's memory using specially crafted
inputs.  These mistakes arise in lower-level languages that do not
provide memory safety guarantees, such as C, and can be partially
mitigated by a wide range of techniques, for example static analysis,
dynamic instrumentation, and address space layout randomization, that
make it more difficult for an adversary to exploit these bugs.
Nail helps developers using lower-level languages to avoid these bugs
in the first place.

The second class, which occurred four times in our study,
is logic errors, where application code
misinterprets input data. Safe languages and exploit mitigation technologies do not help against
such vulnerabilities. This can lead to serious security consequences when two systems disagree on
the meaning of a network packet or a signed message, as shown by the vulnerabilities we described
before. CVE-2013-0211 shows that logic errors can be the underlying cause of memory corruption, when
one part of a parser interprets a size field as a signed integer and another interprets it as an
unsigned integer. CVE-2013-7338 is a logic error that allows an attacker to craft ZIP files that are
incorrectly extracted or result in application hangs with applications using a Python ZIP library,
because this library does not check that two fields that contain the size of a file contain the same value.
The Android ZIP file signature verification bug that we described
earlier was also among these 4 vulnerabilities.
